---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# autocruller

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/autocruller)](https://CRAN.R-project.org/package=autocruller)
[![R-CMD-check](https://github.com/samherniman/autocruller/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/samherniman/autocruller/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

Auto __ˈɔːtəʊ__ - [short for automobile, a car](https://en.wiktionary.org/wiki/auto)
Cruller __ˈkrʌl ər__ [a pastry roll or bun](https://en.wiktionary.org/wiki/cruller)

autocruller - car bun

{autocruller} allows one to download, manipulate and visualize CO^2^ readings from the
[indoorco2map.com](https://indoorco2map.com/?lat=51.16570&lng=10.45150&zoom=6.00) dataset. 

Please support that project by contributing CO^2^ readings, reporting bugs, telling your friends and financially supporting it (if you feel inclined).

## Carbon Dioxide is important, Y'all

## Never used R before?

Read [this](https://rstudio-education.github.io/hopr/starting.html#starting)

## Installation

You can install the development version of autocruller from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("samherniman/autocruller")
```

## Get started

Download the latest data with `ac_get_co2()`

```{r getco2}
library(autocruller)

ac_df <- ac_get_co2()
```

That will give you a dataframe with all the current CO^2^ measurements. 

```{r glimpse}
dplyr::glimpse(ac_df)
```

If you want the co2arrays to be in long format, you can do this:

```{r}
ac_df_long <- tidyr::unnest_longer(ac_df, co2array) 
```


## Make a graph

```{r eval=FALSE}
pak::pak("tidyplots")
```

You can compare averages with the wide format data

```{r}
library(tidyplots)

types_c <- c(
  "arts_centre","events_centre", "cinema",
  "social_facility", "theatre", "music_venue",
  "music","nightclub" , "social_centre", "concert_hall"
)
ac_df |> 
  dplyr::filter(osmtag %in% types_c) |> 
tidyplot(
         x = ventilation, 
         y = ppmavg,
         color = ppmavg) |> 
  add_data_points_beeswarm(size = 3) |> 
  adjust_y_axis(transform = "log2") |> 
  adjust_size(width = NA, height = NA, unit = "cm") |> 
  adjust_font(fontsize = 16) |> 
  adjust_x_axis_title("Ventilation system on?") |> 
  adjust_y_axis_title("CO2 ppm average") |> 
  remove_legend() |> 
  adjust_title("CO2 Averages at music venues") |> 
  adjust_caption("Data from indoorCO2map.com")
```

And track things over time with the long format data

```{r}
ac_df_long |> 
  dplyr::filter(.id == 127) |>
  dplyr::mutate(
    measurement_sequence = dplyr::row_number()
  ) |> 
tidyplot(
         x = measurement_sequence, 
         y = co2array,
         color = co2array) |> 
  add_data_points() |> 
  adjust_size(width = NA, height = NA, unit = "cm") |>
  adjust_font(fontsize = 16) |>
  adjust_x_axis_title("Time") |> 
  adjust_y_axis_title("CO2 ppm") |> 
  remove_legend() |> 
  adjust_title("CO2 measurements at recording 127") |> 
  adjust_caption("Data from indoorCO2map.com")
```

